---
title: "Homework 1"
output: github_document
---

## Problem 1

This problem focuses the use of inline R code, plotting, and the behavior of `ggplot` for variables of different types.

# Loading the Library and Dataset

Load the moderndive and tidyverse libraries (for scatter plot later):
```{r}
library(moderndive)
library(tidyverse)
```

Load the early_january_weather dataset:
```{r}
data("early_january_weather")
```

# Describing the Dataset

Get an overview of the dataset (although str('df') displays the number of rows and columns in the dataframe, also using nrow and ncol as directed):
```{r}
str(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
```

This dataset describes the weather in the first two weeks of January 2013. It contains 358 observations (rows) and has 15 variables (columns), including temperature, humidity, and visibility.

Find the mean temperature:
```{r}
mean(early_january_weather$temp)
```

The mean temperature is 40 degrees F. 

# Making a Scatterplot

Make a scatterplot of time_hour(x) vs. temp(y), with the points colored by humidity: 

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
```

Exporting the scatterplot to the project directory:
```{r}
ggsave("TempvsTime.png")
```



