---
title: "Homework 1"
output: github_document
---

# Problem 1

## Loading the Library and Dataset

Load the `moderndive` and `tidyverse` libraries (for scatterplot later):
```{r}
library(moderndive)
library(tidyverse)
```

Load the `early_january_weather` dataset:
```{r}
data("early_january_weather")
```

## Describing the Dataset

Get an overview of the dataset (although str('df') displays the number of rows and columns in the dataframe, also using nrow and ncol as directed):
```{r}
str(early_january_weather)
nrow(early_january_weather)
ncol(early_january_weather)
```

This dataset describes the weather in the first two weeks of January 2013. It contains 358 observations (rows) and has 15 variables (columns), including temperature, humidity, and visibility.

Find the mean temperature:
```{r}
mean(pull(early_january_weather, var = temp))
```

The mean temperature is approximately 40 degrees F. 

## Making a Scatterplot

Make a scatterplot of time_hour(x) vs. temp(y), with the points colored by humidity: 

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
```

The plot depicts temperatures generally trending upwards throughout the first two weeks of January, until a sudden cold spell mid-month. Humidity varies throughout the month, but is noticeably higher when temperatures sit above the low 40s. Daily cycles from the high temp in the middle of the day to the low at night are also clear. 

Exporting the scatterplot to the project directory:
```{r}
ggsave("TempvsTime.png")
```

# Problem 2

## Creating a Data Frame
Create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r}
problem2_df = tibble(
    vec_random = rnorm(10),
    vec_logical = vec_random > 0,
    vec_char = c("Hoyt", "Bond", "Atlantic", "Smith", "Remsen", "Court", "Pacific", "Boerum", "Livingston", "Fulton"),
    vec_factor = factor(c("Street", "Street", "Avenue", "Street", "Place", "Street", "Avenue", "Place", "Avenue", "Street"))
)
```

View the resulting data frame:
```{r}
problem2_df
```

## Calculating Means

Take the mean of each variable in the dataframe:
```{r}
mean(pull(problem2_df, var = vec_random))
mean(pull(problem2_df, var = vec_logical))
mean(pull(problem2_df, var = vec_char))
mean(pull(problem2_df, var = vec_factor))
```

I am able to determine that the mean value of the random sample and logical vectors, but trying to take the mean of the character and factor vectors doesn't work.

## Calculating Means Attempt 2: Converting Variables

Attempt to convert the logical, character, and factor vectors into numeric variables:
```{r, results = 'hide', warning = FALSE}
vec_logical_num = as.numeric(pull(problem2_df, var = vec_logical))
vec_char_num = as.numeric(pull(problem2_df, var = vec_char))
vec_factor_num = as.numeric(pull(problem2_df, var = vec_factor))
```

As a result, the logical vector now has values of 1 and 0, with 1 corresponding to previous True values and 0 corresponding to previous False values. This is how a mean of the logical vector was calculated before, by just finding the average of the 10 values of 1s and 0s.

The character vector just has 10 values of NA, as the strings previously present didn't contain any actual numbers. This explains why we weren't able to calculate a mean for this vector, as it contains no values that R can interpret numerically. 

Finally, the factor vector turns into a vector of 1, 2, and 3, with each corresponding to the factor "level" of the item at that position previously. For example, the Street "level" became 3. I presume that we can't get the mean of the factor vector because the 1,2,and 3 values are just assigned to represent true categories behind the scenes. 
